Preprocessing

### 2024-08-09 nbs/guides/preprocessing/preprocessing.qmd
chore(nbs): add gitignore
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

>>>>

# Download data

```{python}
# | label: download-data
import polars as pl
import altair as alt

alt.data_transformers.enable("vegafusion")

flights = pl.read_parquet(
    "https://vegafusion-datasets.s3.amazonaws.com/vega/flights_1m.parquet"
)
```

# Make plots

```{python}
# | label: make-plots
delay_hist = (
    alt.Chart(flights)
    .mark_bar()
    .encode(alt.X("delay", bin=alt.Bin(maxbins=30)), alt.Y("count()"))
)
delay_hist
```
